
% references.tex
%Curriculum Vitae, Weiwei Chen, 11/12/12 first version

% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008-2012 Nathaniel Johnston <nathaniel@njohnston.ca> http://www.njohnston.ca
% (c) 2012	Weiwei Chen <weiwei.chen@uci.edu> http://www.cecs.uci.edu/~weiweic
%
% Depending on your TeX distribution, you may need to download the revnum and longtable packages for this template to work!
%
%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.
%\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{POTENTIAL REFERENCES}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Dr. Rainer D\"{o}mer (Ph.D. Advisor) \\
Associate Professor\\
Electrical Engineering and Computer Science\\
University of California, Irvine\\
%+1 (949) 824-9007\\
%\href{mailto:doemer@uci.edu}{doemer@uci.edu}\\
\vspace{5mm}

Dr. Daniel Gajski \\
Professor, Founding Director\\
Center for Embedded Computer Systems\\
University of California, Irvine\\
%+1 (949) 824-4155\\
%\href{mailto:gajski@uci.edu}{gajski@uci.edu}\\
\vspace{5mm}

Dr. Fadi Kurdahi\\
Professor, Director\\
Center for Embedded Computer Systems\\
University of California, Irvine\\
\vspace{5mm}

Dr. Calin Cascaval\\
Senior Director, Engineering \\
Qualcomm Research Silicon Valley \\
\vspace{5mm}

Prof. Dr. Wolfgang Rosenstiel\\
Dean, Faculty of Science \\
University of T\"{u}bingen, Germany \\
\vspace{5mm}

Prof. Dr.-Ing. Wolfgang Nebel \\
Professor \\
Computer Science (Informatik) Department \\
The Carl von Ossietzky University of Oldenburg, Germany\\
\vspace{5mm}

Prof. Sridevan Parameswaran \\
Professor,  Program Director  for Computer Engineering \\
School of Computer Science and Engineering \\
University of New South Wales, Australia \\
\vspace{5mm}

Dr. Ajit Dingankar \\
Principal Engineer at Intel \\
\vspace{5mm}

Dr. Desmond Kirkpatrick \\
Principal Engineer at Intel \\
\vspace{5mm}

Prof. Petru Eles \\
Professor of Embedded Computer Systems, Deputy Chairman\\
Department of Computer and Information Science (IDA) \\
Link\"{o}ping University,  Sweden\\
\vspace{5mm}

Prof. Soonhoi Ha \\
Professor \\
Computer Engineering Department \\
Seoul National University, South Korea \\
\vspace{5mm}

Prof. J\"{o}rg Henkel \\
Professor, Chair for Embedded Systems \\
Karlsruhe Institute of Technology, Germany \\
\vspace{5mm}

Prof. Lothar Thiele \\
Professor  \\
Computer Engineering and Networks Laboratory  \\
Swiss Federal Institute of Technology Zurich, Switzerland \\
\vspace{5mm}

Prof. Dr.-Ing. Dr. h.c. Gerhard Fettweis  \\
Vodafone Chair Mobile Communications Systems \\
Dresden University of Technology \\
\vspace{5mm}

Prof. Giovanni De Micheli  \\
Professor and Director  \\
The Institute of Electrical Engineering and The Integrated Systems Centre \\
Swiss Federal Institute of Technology in Lausanne (EPFL), Switzerland \\
\vspace{5mm}

Prof. Dr.-Ing. J\"{u}rgen Teich \\
Professor, Chair for Hardware-Software-Co-Design \\
Department of Computer Science \\
University of Erlangen-Nuremberg, Germany \\
\vspace{5mm}

Prof. Dr. Peter Marwedel \\
Professor   \\
Head of Design Automation for Embedded Systems Group  \\
Technical University of Dortmund  \\
\vspace{5mm}


Prof. Dr. Oliver Bringmann \\
Professor, Chair  \\
Embedded Systems at the Department of Computer Science  \\
The University of T\"{u}bingen, Germany \\
Director  \\
FZI Research Center for Information Technologies in Karlsruhe, Germany \\
\vspace{5mm}
